### 2024-07-26 conteudo/background/codeduplication.tex
Add Type Figures

\begin{itemize}
	\begin{item}
		\textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. 
		(ADD FIGURE) shows a typical example of Type-1 Code 
		Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2:} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes.
		(ADD FIGURE) shows a typical example of Type-2 Code Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3:} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. (ADD FIGURE) shows a typical example of 
		Type-3 Code Duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4:} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition.
		(ADD FIGURE) shows a typical example of Type-4 Code Duplication \citep{litreview}. 
	\end{item}

@@

>>>>

\begin{itemize}
	\begin{item}
		\textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2:} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3:} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4:} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}

@@

\begin{figure}
\includegraphics[scale=0.38]{types/type1}
\caption{Example of Type-1 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type2}
\caption{Example of Type-2 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type2}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type3}
\caption{Example of Type-3 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type3}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type4}
\caption{Example of Type-4 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type4}
\end{figure}
